Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-08-02 ident_manu.tex
working on parmtab function

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Tue Aug 1 13:06:48 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/8169e808436dd5e6f70a58cb58addf7a41d98b7b}{8169e808436dd5e6f70a58cb58addf7a41d98b7b}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

\caption{Sensitivity of \ac{do} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.02$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.02$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline

@@

~~decay rate of CDOM, 1/day&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline

@@

\caption{Sensitivity of ammonium to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect ammonium are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:nh4sens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.6$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.29$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.5$\tabularnewline
~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline

@@

~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.07$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of \ac{chla} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{chla} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:chlsens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.62$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.25$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of irradiance to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect irradiance are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:irrsens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.04$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.02$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.04$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline

@@

~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.05$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline

@@

\caption{Sensitivity of nitrate to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect nitrate are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:no3sens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.7$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.2$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.7$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline

@@

~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$0.07$\tabularnewline
~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.04$\tabularnewline

@@

\caption{Sensitivity of \ac{pom} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \ac{pom} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om1sens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.67$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.22$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.39$\tabularnewline
~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of \acl{dom} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect \acl{dom} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om2sens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.85$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.41$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline

@@

~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.1$\tabularnewline

@@

~~half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of phosphate to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output from the default (see \cref{l1}).  Parameters that did not affect phosphate are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:po4sens}} 

@@

~~Optimum temperature for growth(C)&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline

@@

~~initial slope of the photosynthesis-irradiance relationship&\textit{alpha}&$0.23$\tabularnewline

@@

~~Phytoplankton threshold for grazing, is multiplied by VOLcell&\textit{Athresh}&$0.13$\tabularnewline

@@

~~Zooplankton mortality constant for quadratic mortality&\textit{Zm}&$0.35$\tabularnewline

@@

~~proportion of grazed phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
~~Zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
~~Zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline

@@

~~decay rate of CDOM, 1/day&\textit{KGcdom}&$0.02$\tabularnewline

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Wed Aug 2 13:16:06 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/5cd8b68899d08c2c8f96177fe72e018bd764f96a}{5cd8b68899d08c2c8f96177fe72e018bd764f96a}\newline Acronyms: \acfi{chla}; \acfi{cgem}; \acfi{do}; \acfi{dom}; \acfi{gom}; \acfi{lcs}; \acfi{marb}; \acfi{pom}; \acfi{rmse}; \acfi{zerod}}

@@

\caption{Sensitivity of \ac{do} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect \ac{do} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:dosens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.02$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.02$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$4.57\times 10^{-3}$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.02$\tabularnewline

@@

~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$7.78\times 10^{-3}$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$5.32\times 10^{-3}$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$2.96\times 10^{-3}$\tabularnewline

@@

~~decay rate of CDOM&\textit{KGcdom}&$2.98\times 10^{-3}$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$5.8\times 10^{-4}$\tabularnewline

@@

\caption{Sensitivity of ammonium to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect ammonium are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:nh4sens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.79$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.6$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.29$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.5$\tabularnewline
~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.3$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.22$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.16$\tabularnewline

@@

~~decay rate of CDOM&\textit{KGcdom}&$0.07$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$7.55\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of \ac{chla} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect \ac{chla} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:chlsens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.6$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.62$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.25$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.41$\tabularnewline
~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.23$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.14$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$1.19\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of irradiance to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect irradiance are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:irrsens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.03$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.04$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.02$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.04$\tabularnewline

@@

~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.02$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.01$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$9.67\times 10^{-3}$\tabularnewline

@@

~~decay rate of CDOM&\textit{KGcdom}&$0.05$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$6.18\times 10^{-5}$\tabularnewline

@@

\caption{Sensitivity of nitrate to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect nitrate are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:no3sens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.3$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.7$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.2$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.7$\tabularnewline

@@

~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.26$\tabularnewline

@@

~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.1$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$0.07$\tabularnewline
~~decay rate of CDOM&\textit{KGcdom}&$0.04$\tabularnewline

@@

\caption{Sensitivity of \ac{pom} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect \ac{pom} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om1sens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.86$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.67$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.22$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.39$\tabularnewline
~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.27$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.16$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.12$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$3.72\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of \acl{dom} to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect \acl{dom} are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:om2sens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$1.48$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.85$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.41$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.17$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.13$\tabularnewline
~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.12$\tabularnewline

@@

~~decay rate of CDOM&\textit{KGcdom}&$0.1$\tabularnewline

@@

~~half-saturation concentration for denitrification&\textit{KNO3}&$3.16\times 10^{-3}$\tabularnewline

@@

\caption{Sensitivity of phosphate to perturbations of individual parameters.  Sensitivities are based on a 50\% increase from the initial parameter value, where $L1$ summarizes differences in model output (see \cref{l1}).  Parameters that did not affect phosphate are not shown.  Parameters are grouped by categories as optics, temperature, phytoplankton, zooplankton, and organic matter.\label{tab:po4sens}} 

@@

~~Optimum temperature for growth&\textit{Tref(nospA+nospZ)$_{p1}$}&$0.16$\tabularnewline

@@

~~initial slope of photosynthesis v irradiance&\textit{alpha}&$0.23$\tabularnewline

@@

~~phytoplankton threshold for grazing&\textit{Athresh}&$0.13$\tabularnewline

@@

~~quadratic mortality constant&\textit{Zm}&$0.35$\tabularnewline

@@

~~proportion of phytoplankton lost to sloppy feeding&\textit{Zslop}&$0.15$\tabularnewline
~~zooplankton growth-dependent respiration factor&\textit{Zrespg}&$0.1$\tabularnewline
~~zooplankton biomass-dependent respiration factor&\textit{Zrespb}&$0.06$\tabularnewline

@@

~~decay rate of CDOM&\textit{KGcdom}&$0.02$\tabularnewline
